Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning

### 2020-09-27 2_revisions/V0_Before submission/V0_3_1_Second draft/tmp-emotion_V0_3.tex
First data commit: V2-1, before second review

\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with text-mining}

@@

Up until recently, most studies in tourist behavior have been biased for the Western world. With the increase of Chinese outbound tourists to countries across the globe, academic interest for this group has risen. However, cross-cultural studies of their differences with other cultures are scarce and predate the current boom in the Chinese economy. This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels. Additionally, most studies choose certain factors to be analyzed in their questionnaire, and this often is limited to managerial attributes of the hotel. With the spread of the use of Web 2.0 to write online reviews of hotels, a large amount of text data is available for research purposes. With text mining, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers. This means that we can measure just how important are certain attributes of the hotel to customers, and whether those are managerial or environmental, that is, internal or external to the hotel. In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which can be used for top-weighted ranked lists with different elements and lengths. We found that Chinese customers prefer big and clean spaces and that Western customers are satisfied with friendly staff members. We also found that Chinese tourists are unsatisfied with the hotel being Chinese friendly with treatment and language and that Western customers are unsatisfied with rooms that they consider dirty, or that smell of cigarette.

@@

Recently, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), with approximately a fourth of the total (25.63\%) coming from China. Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.

@@

With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}. Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more. Data mining and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines. This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.

@@

The objective of this study is to determine the difference in preferences between Chinese-speaking and English-speaking customers of Japanese hotels using text-mining techniques. We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure. Furthermore, we aim to measure if both customer groups have differences in priorities for the factors that are common to both groups. Furthermore, we aim to measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.

@@

\begin{hyp}
\label{hyp:1}
Chinese and Western tourists have different satisfaction and dissatisfaction factors.
\end{hyp}

@@

% In our corpus, there were \num[group-separator={,}]{23443} different words used, from which \num[group-separator={,}]{2802} were noise characters.

@@

Because Chinese text doesn't have spaces, to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

@@

The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}. A group of keywords is determined by a calculation and comparison of Shannon's entropy \cite[][]{shannon1948} between two classes, and then the keywords are used in a Support Vector Classifier \cite[][]{cortes1995}, optimizing the entropy comparison values to select the best performing classifier. The selected classifier's feature keywords would then clearly represent the user preferences leading to positive and negative emotions.

Shannon’s entropy, in the field of Information Theory, is defined to be the expected value of the information content in a signal. It is shown in formulas \ref{eq:H} and \ref{eq:lim_H}. Using this value we can observe the probability distribution of each word inside the corpus. A word that is included in many documents will have a high entropy value for that set of documents. Opposite to this, a word appearing in only one document will have an entropy value of zero. We show this concept in Figure \ref{fig:entropygraphs}.

\begin{equation}\label{eq:H}
H = - \sum_{i=1}^M [P \log_2 P]
\end{equation}

\begin{equation}\label{eq:lim_H}
\lim_{P\to0+} P \log_2 P = 0
\end{equation}

\begin{figure}[bp]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\linewidth]{entropyzero.png}
        \caption{Entropy close to zero.}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\linewidth]{entropyhigh.png}
        \caption{High entropy}
    \end{subfigure}
\caption{Probabilities of a word j being contained in a document i.}
\label{fig:entropygraphs}
\end{figure}

To apply this logic, we retrieved 50 reviews as a sample of our corpus and with the collaboration of a group of 5 Chinese students, which were split into 159 sentences. We then tagged each sentence as the classes positive or negative depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class. In the case of English reviews, we sampled 665 reviews and with the collaboration of English-speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences. Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels. This is shown in formula \ref{eq:entropy_pos}. Likewise, words with higher entropy for the dissatisfaction set than the satisfaction set by a factor of \(\alpha'\) were determined to be keywords tied to dissatisfaction in our texts. This is shown in formula \ref{eq:entropy_neg}. Examples of positive and negative sentences in English and Chinese are shown in the Appendix, in Table \ref{tab:training_examples}.

\begin{equation}\label{eq:entropy_pos}
H_{P} > \alpha H_{N} % \rightarrow satisfaction \: keyword
\end{equation}

\begin{equation}\label{eq:entropy_neg}
H_{N} > \alpha' H_{P} % \rightarrow dissatisfaction \: keyword
\end{equation}

The mutually independent coefficients \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25. The result was 40 lists for each language, 20 for each emotional class. We trained a different Support Vector Classifier with each of the lists, and we chose the best performing lists for each emotional class and then combined the successful lists to train our best performing classifier. This resulted in a best performing positive emotion classifier (positive/non-positive) for each language.

For the performance tests, we used a 5-fold cross-validation \cite[][]{kohavi1995} process in the Chinese reviews, and a 10-fold cross-validation process in the English reviews case, in which we calculated their F-measure \cite[][]{powers2011} means and standard deviations. The number of \(k\)-folds was decided from the sample size. Table \ref{tab:svm_f1_zh} shows the lists that had the best performance results in the case of Chinese text and Table \ref{tab:svm_f1_en} shows the best performance results in English texts in the Appendix.

We then used these best performing classifiers in the rest of the respective data to label positive emotion sentences in a binary manner. The sentences not belonging to the positive emotion class were considered to belong in the negative emotion class. This resulted in \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.

@@

During the SVM learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly. These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those contained in the support vectors, close to the separating hyperplane. Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process. Below we show the formula for the weight vector (\ref{eq:svm_weight}).

@@

In order to calculate the similarity between the ranked lists shown in Tables \ref{tab:pos_keys_zh} and \ref{tab:pos_keys_en}, and the lists in Tables \ref{tab:neg_keys_zh} and \ref{tab:neg_keys_en}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points. Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis. For example, in the English keyword lists, the word is 'pricey' while in the Chinese keywords it is translated as 'price', and as such, it was changed to 'pricey' to match the English keywords. The results of this are shown in Table \ref{tab:rbo}. In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points bigger than 7, and then it is cut at the cutoff point of 5. Since the RBO measure can work regardless of the length of each list, this is not a problem in its calculation.

@@

\subsection{Chinese tourists' satisfaction and dissatisfaction keywords}

Analyzing satisfaction keywords of Chinese hotel reviews from Table \ref{tab:pos_keys_zh}, we found that the most relevant subjects Chinese customers perceive positively are cleanliness and size, very possibly of the room they had stayed in. There is also the possibility that reviewers were praising, in general, the cleanliness of Japan’s environment, streets without litter, potable water and their culture of respecting spaces. Our results also indicate that the closeness of the hotel to scenic places is highly preferred by Chinese customers. Lower in the list of priorities, other positive factors that come into play when Chinese tourists choose a hotel to stay are the location in relation to public transport availability (such as the subway); and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping.

Regarding dissatisfaction keywords in Table \ref{tab:neg_keys_zh}, we found that the most frequently criticized aspect of Japanese hotels was the price. Another important negative factor can be the availability or lack thereof of Chinese translations. Chinese customers can feel lost when they don't understand directions or instructions, either written or spoken; however, according to our data, most customers can be thought to have complained about written translations. Another dissatisfaction factor is the word 'old', which can be referring to the age of the building, or the general design and look of the place being old-fashioned.

We can assert that Chinese customers value the room quality over transportation availability, that they are interested in included breakfast with the hotel stay, that they are concerned with value for money and the availability of Chinese language translations to have an easier time in the accommodation.

\subsection{English-speaking tourists' satisfaction and dissatisfaction keywords}

The most important satisfaction keyword in English reviews (see Table \ref{tab:pos_keys_en}) is 'staff', while lower in the list we can also observe 'helpful' and 'friendly', possibly referring to the staff as well, and since Japan is famous for its customer service culture, this is not unexpected. Next on the list, we can observe they value cleanliness, but a few more items in the list are regarding the location of the hotel, and possibly the availability of nearby transportation, such as the subway or train. We can also observe that the word 'free' is present there, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.

The negative keywords of dissatisfied customer reviews (see Table \ref{tab:neg_keys_en}) reveal an interesting picture. While the most used keyword is also related to the price of the hotels, most of the keywords are related to the hygiene of the hotel, namely dirty carpets, stains, cigarette smell in the room or curtains, and so on. We can also observe that the word 'renovation' is written lower in the list, as well as the word 'paper'. After observation of the samples, it is often used with the expression 'paper-thin walls', which could mean the customers can hear their neighbors easily. Regarding the word 'renovation', some cities in Japan (e.g. Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities. Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences. Another keyword there is 'slow', which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.

We can assert that English-speaking tourists value staff friendliness and location convenience concerning transport, but are concerned about any kind of decline in room quality both visually and regarding the smell and air quality, being quick to judge any sort of remains of cigarette smell.

@@

% USE Results from Rank-biased Overlap (full list) experiment results_p_0.9_cutoff_10.txt

The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists at different cutoff points, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values. This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well. This confirms our hypothesis \ref{hyp:1}, that the satisfaction and dissatisfaction factors are different for Chinese and English-speaking tourists.

@@

The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that 'clean', 'recommend', 'subway' and 'price' are common satisfaction and dissatisfaction factors to both customer groups accordingly. Furthermore, their place in the ranked list is the same for 'clean', 'subway' and 'price', making only 1 out of 4 factors different in priority. This means hypothesis \ref{hyp:2} is rejected, where even the similar aspects in both customer groups were hypothesized to be different in their priority.

@@

As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature. For the satisfaction factors of Chinese-speaking tourists, 30\% of the keywords are managerial factors, while 60\% of them are environmental factors ('recommendation' is not counted as either). On the other hand, for the satisfaction factors of English-speaking tourists, 60\% of them are managerial, while 30\% of them are environmental. Now, for the dissatisfaction factors of Chinese customers, 71.4\% of them are managerial while the remaining 28.6\% of them are environmental. On the other hand, a 100\% of the dissatisfaction factors for English-speaking customers are managerial in nature. We can see these results in Table \ref{tab:hyp3}. The interpretation of these keywords is shown in the Appendix in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.

@@

From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services. The word 'staff' is the most frequently used word for satisfied customers, while 'helpful' and 'friendly' follow it lower in the list at the 4th and 6th place. Japan is famous for their customer service all over the world. Staff members are trained to speak in \textit{sonkeigo}, or 'respectful language', one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say 'Please, allow me to guide you', and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well. This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively. After all, Japanese staff treats all customers in this respectful manner, but for some customers, this could very well be the best they have been treated until that moment. We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists.

However, we can see from the rest of the keywords in combination that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness. Where Chinese customers were completely satisfied, English-speaking customers have found many places unacceptable to their standards. The most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains. \cite{kozak2002} also found that hygiene and cleanliness were important satisfaction determinants for Western tourists. However, in the previous literature, this was linked merely to satisfaction. In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts.

@@

In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via a Support Vector Classifier. We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof). We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points. These are low values, so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.

We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ('clean', 'recommend', 'subway' and 'price'), only one of the words ('recommend') had a different place in the ranking of the lists for either group. This means our hypothesis \ref{hyp:2} is rejected, and that the common ground within both customer groups is also similar in ranking.

@@

During our research, apart from the group of Chinese students that collaborated with the training data and emotion tagging process, we received the commentary and discussion necessary to understand certain
cultural aspects that could influence the interpretation of the data, from empirical and anecdotal Chinese sources, as well as collaboration in understanding the meaning behind the words we extracted by our dear colleagues, whom we would like to show gratitude to, Mr. Zhou Liangyuan, Ms. Fan Min and Ms. Eerdengqiqige.

@@

% \section*{References}

@@

\section{Sentiment analysis training data examples}

@@

\section{Entropy keyword extraction experiment results}

@@

\section{Keywords with high SVM weights regardless of frequency}

@@

\section{Managerial and Environmental keywords}

In section \ref{disc:hyp3}, we discussed how satisfaction of the customer can come both from managerial attributes of the hotel, as well as environmental attributes. We identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}. The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.

>>>>

\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning}

@@

Up until recently, most studies in tourist behavior have been biased for the Western world. With the increase of Chinese outbound tourists to countries across the globe, academic interest for this group has risen. Increasing variation amongst clients means that managing hotels in a way that caters to their different tastes becomes more and more important. Despite this, cross-cultural studies of differences between Asian and Western cultures are scarce and predate the current boom in the Chinese economy. This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels. Additionally, most studies choose certain factors to be analyzed in their questionnaire, and this often is limited to managerial attributes of the hotel. With the spread of Web 2.0 and online hotels reviews, a large amount of text data is available for research purposes. With our method, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers. This means that we can measure just how important are certain attributes of the hotel to customers, and whether those are managerial or environmental, that is, internal or external to the hotel. In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which can be used for top-weighted ranked lists with different elements and lengths. We found that Chinese customers prefer big and clean spaces and that Western customers are satisfied with friendly staff members. We also found that Chinese tourists are unsatisfied with the hotel being Chinese friendly with treatment and language and that Western customers are unsatisfied with rooms that they consider dirty, or that smell of cigarette.

@@

Recently, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), with approximately a fourth of the total (25.63\%) coming from China. Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}. With these and other multicultural tourists populations, the tourist market is more and more diverse. Diversity in customers cultural backgrounds means that their expectations when staying at a hotel will also be varied. Hotel management therefore needs to cater to these different needs and expectations to increase their customers' satisfaction and maintain a good reputation generating positive word-of-mouth.

@@

With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}. Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more. Data mining, machine learning and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines. This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.

@@

The objective of this study is to determine the difference in preferences between Chinese-speaking and English-speaking customers of Japanese hotels using text-mining techniques. We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure. Furthermore, we will measure if both customer groups have differences in priorities for the factors that are common to both groups. In addition, we also measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.

@@

\begin{hyp}
\label{hyp:1}
Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
\end{hyp}

@@

@@

In order to parse Chinese words and separate them we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

@@

The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier. The selected SVM's keywords would then clearly represent the user preferences leading to positive and negative emotions. Examples of tagged sentences are shown in Table \ref{tab:training_examples}, and SVM performance results are shown in section \ref{apx:entropy_results}.

Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus. A word that is included in many documents will have a high entropy value for that set of documents. Opposite to this, a word appearing in only one document will have an entropy value of zero.

We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative. The entropy comparison factor was tested from 1.25 to 6 in intervals of 0.25. After classification, our data contained \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.

@@

During the SVM learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly. These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those close to the separating hyperplane. Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process. Below we show the formula for the weight vector (\ref{eq:svm_weight}).

@@

In order to calculate the similarity between the ranked lists shown in Tables \ref{tab:pos_keys_zh} and \ref{tab:pos_keys_en}, and the lists in Tables \ref{tab:neg_keys_zh} and \ref{tab:neg_keys_en}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points. Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis. For example, in the English keyword lists, the word is 'pricey' while in the Chinese keywords it is translated as 'price', and as such, it was changed to 'pricey' to match the English keywords. The results of this are shown in Table \ref{tab:rbo}. In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5. Since the RBO measure can work regardless of the length of each list, this is not a problem in its calculation.

@@

@@

The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)). This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well. This confirms our hypothesis \ref{hyp:1}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.

@@

The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that 'clean', 'recommend', 'subway' and 'price' are common factors to both customer groups. Their place in the ranked list is the exact same for most of them, and only 1 out of 4 factors is different in rank. Furthermore, when arranging both lists by eliminating all uncommon elements, the lists become identical with an RBO of 1.0 for both satisfaction and dissatisfaction lists. This means hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), where the similar aspects in both customer groups were hypothesized to be different in their priority.

@@

As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature. We can see these results in Table \ref{tab:hyp3}. The interpretation of these keywords is shown in the Appendix in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.

@@

From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services. The word 'staff' is the most frequently used word for satisfied customers, while 'helpful' and 'friendly' follow it lower in the list at the 4th and 6th place. Japan is famous for their customer service all over the world. Staff members are trained to speak in \textit{sonkeigo}, or 'respectful language', one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say 'Please, allow me to guide you', and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well. This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively. After all, Japanese staff treats all customers in this respectful manner, but for some customers, this could very well be the best they have been treated until that moment. We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists. On another note, we can also observe that the word 'free' is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.

However, we can see from the rest of the keywords in combination that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness. Where Chinese customers were completely satisfied, English-speaking customers have found many places unacceptable to their standards. The most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains. \cite{kozak2002} also found that hygiene and cleanliness were important satisfaction determinants for Western tourists. However, in the previous literature, this was linked merely to satisfaction. In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts. Aside from cleanliness, we can also observe the word 'renovation' is written lower in the list, as well as the word 'paper'. After observation of the samples, it is often used with the expression 'paper-thin walls', which could mean the customers can hear their neighbors easily. Regarding the word 'renovation', some cities in Japan (e.g. Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities. Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences. Another keyword there is 'slow', which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.

@@

In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via a Support Vector Classifier. We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof). We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points. These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.

We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ('clean', 'recommend', 'subway' and 'price'), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0. This means our hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.

@@

During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr. Zhou Liangyuan, Ms. Fan Min and Ms. Eerdengqiqige. We would also like to show gratitude to Ms. Jajus Aleksandra, from whom we also received notes on the editing and commentary on the content of our manuscript.

@@

\section*{References}

@@

\section{Sentiment analysis training data examples}\label{apx:sentences_ex}

@@

\section{Entropy keyword extraction experiment results}\label{apx:entropy_results}

@@

\section{Keywords with high SVM weights regardless of frequency}\label{apx:keywords_weights}

@@

\section{Managerial and Environmental keywords}\label{apx:man_env}

As explained on \ref{disc:hyp3}, we identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}. The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.
